02_DESeq_characterization

### 2019-08-13 analysis/03_DESeq2_characterization.Rmd
new musical genes
eval = F for all the things :(

```{r setup, message=F, comment=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library("ggimage")

@@

## plot raw counts

```{r musicalgenes, cache = T, eval=T}
head(countData)
head(geneinfo)

candidataCounts <- countData
candidataCounts$Name <- row.names(candidataCounts)
candidataCounts <- candidataCounts %>%
  filter(Name %in% c("NP_990797.2", "NP_001138861.1"))
row.names(candidataCounts) <- candidataCounts$Name
candidataCounts$Name <- NULL
candidataCountsT <- t(candidataCounts)
candidataCountsT <- as.data.frame(candidataCountsT)

candidataCountsT$entrez <- row.names(candidataCountsT)
colData$entrez <- row.names(colData)

candidataCountsTcol <- full_join(colData, candidataCountsT)

str(candidataCountsTcol)

candidataCountsTcol2 <- candidataCountsTcol %>%
  group_by(sextissue, treatment) %>%
  summarize(GAL = mean(NP_001138861.1, na.rm = TRUE),
            PRL = mean(NP_990797.2, na.rm = TRUE)) %>%
  gather(GAL, PRL, key = "gene", value = "mean")

candidataCountsTcol2 <- as.data.frame(candidataCountsTcol2)

musicgenes <- function(mygroup, mysusbtitle){

myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup)) %>%
ggplot(aes(x = treatment, y = mean)) +
  geom_point(colour = "white") + 
  geom_line(group = 1, color='grey') +
  theme_bw() +
  facet_wrap(~gene, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_image(aes(image="https://storage.needpix.com/rsynced_images/music-34177_1280.png")) +
  labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL)

  return(myplot)

}

a <- musicgenes("female_hypothalamus", "female hypothalamus")
b <- musicgenes("male_hypothalamus", "male hypothalamus")

c <- plot_grid(a,b)
c

pdf("../figures/characterization/musicalgenes-1.pdf", width = 8, height = 6)
plot(c)
dev.off()

musicgenes2 <- function(mygroup, mysusbtitle){

myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup)) %>%
ggplot(aes(x = treatment, y = mean)) +
  geom_point(colour = "white") + 
  theme_bw() +
  facet_wrap(~gene, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_image(aes(image="https://storage.needpix.com/rsynced_images/music-34177_1280.png")) +
  labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL) +

  return(myplot)

}

a <- musicgenes2("female_hypothalamus", "female hypothalamus")
b <- musicgenes2("male_hypothalamus", "male hypothalamus")

c <- plot_grid(a,b)
c

pdf("../figures/characterization/musicalgenes-2.pdf", width = 8, height = 6)
plot(c)
dev.off()

```

@@

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9")
group2 <- group1

a <- plottotalDEGschar(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGschar(dds.female_pituitary, "female pituitary")
c <- plottotalDEGschar(dds.female_gonad, "female gonad")
d <- plottotalDEGschar(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGschar(dds.male_pituitary, "male pituitary")
f <- plottotalDEGschar(dds.male_gondad, "male gonad")

@@

```{r pca}
plotPCAs(dds.female_hypothalamus, "female hypothalamus")
plotPCAs(dds.female_pituitary, "female pituitary")      
plotPCAs(dds.female_gonad, "female gonad")
plotPCAs(dds.male_hypothalamus, "male hypothalamus")
plotPCAs(dds.male_pituitary, "male pituitary")
plotPCAs(dds.male_gondad, "male gonad")
```

>>>>

```{r setup, message=F, comment=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library(ggimage)

@@

@@

```{r totalDEGs, eval = F}
#create list of groups for deseq contrasts
group1 <- c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9")
group2 <- group1

a <- plottotalDEGs(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(dds.female_pituitary, "female pituitary")
c <- plottotalDEGs(dds.female_gonad, "female gonad")
d <- plottotalDEGs(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(dds.male_pituitary, "male pituitary")
f <- plottotalDEGs(dds.male_gondad, "male gonad")

@@

```{r pca, eval = F}
plotPCAs(dds.female_hypothalamus, "female hypothalamus")
plotPCAs(dds.female_pituitary, "female pituitary")      
plotPCAs(dds.female_gonad, "female gonad")
plotPCAs(dds.male_hypothalamus, "male hypothalamus")
plotPCAs(dds.male_pituitary, "male pituitary")
plotPCAs(dds.male_gondad, "male gonad")
```
